Merging Datasets Through Deep learning

### 2018-09-05 paper2018/datasets.tex
fixing stuff

\section{Benchmarks}
\label{datasets}
Our benchmarks were derived from Wikidata.  Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.  For company names, we augmented the names and surface forms in Wikidata with data from the SEC \footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.  There were 213106 names for people from the specific dump we extracted, and 70946 names for companies.  The extracted files and the cleansing code are available on our repository. The extracted files however contained significant noise that we cleaned up programmatically.  We describe the cleansing rules for people and for companies separately because they were somewhat different.  In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.  This was not possible for company names.

@@

After cleansing, if a name had no alternate surface forms, they were dropped.  This resulted in 40555 company names with an average of 2.2 names each, and 195422 people's names with an average of 4.69 names each.  Using the triplet selection algorithm we created a set of 10.9 million and 1.04 million triplets for people and companies at training.  The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.

\subsection{Dataset characteristics}
As a baseline, we measured how the anchors, positives and negatives were laid out in vector space based on character embeddings alone.  This gives us a measure of how difficult the problem is for the neural network to learn.  We indexed all the vector embeddings (regardless of test or train) into a nearest neighbors algorithm using the Spotify ANNOY\footnote{\url{https://github.com/spotify/annoy}} implementation.  We then queried the index for the $k$ nearest neighbors of this set, varying $k$ so it was either 20, 100, 500, or 1500 neighbors.  Our primary interest was in recall rates of positives prior to any training, to establish the baseline prior to training.  We also measured the nature of hard negatives as we varied the neighborhoods; i.e., what is the mean distance of negatives from the anchor while we increased neighborhoods, compared to the positive distances.  Figure \ref{people_characteristics} shows the results for the people data.  First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\%.  The difficulty of the problem for reconciling people's names is further highlighted by the distance data.  The mean distance of positives from anchor was 9.05, with a standard deviation of 3.08.  The mean distances of negatives from anchor was 2.73, with a standard deviation of 0.99 for $k$ of 20.  However even for $k$ of 1500, the mean negative distance was 3.64, well below the mean positive distance of 9.05.  The company data show a similar trend, although companies seems to be an easier problem than reconciling people data, as shown in Figure \ref{company_characteristics}.  Recall rate for companies starts at 16\% for a neighborhood size of 20, and is up to 25\% for a neighborhood size of 1500.  Mean negative distance is at 3.05 compared to 4.64 at a neighborhood size of 20, with a standard deviation of 1.44.  At a neighborhood size of 1500, mean negative sizes are slightly higher at 3.86.

>>>>

\section{Benchmarks}
\label{datasets}
Our benchmarks were derived from Wikidata.  Specifically, we used the \textit{also known as} property from Wikidata to get alternate forms for the same entity name for people as well as companies.  For company names, we augmented the names and surface forms in Wikidata with data from the SEC\footnote{\url{https://www.sec.gov/dera/data/financial-statement-and-notes-data-set.html}}, which has former and more recent names for companies.  There were 213,106 names for people from the specific dump we extracted, and 70,946 names for companies.  The extracted files and the cleansing code are available on our repository. The extracted files however contained significant noise that we cleaned up programmatically.  We describe the cleansing rules for people and for companies separately because they were somewhat different.  In the case of people's names, we also augmented the data so the system could learn some common rules that define variants of a person's name.  This was not possible for company names.

@@

After cleansing, if a name had no alternate surface forms, they were dropped.  This resulted in 40,555 company names with an average of 2.2 names each, and 195,422 people's names with an average of 4.69 names each.  Using the triplet selection algorithm we created a set of 10.9 million and 1.04 million triplets for people and companies at training.  The data was then split with a 60-20-20 ratio to provide training, validation and test data respectively.  Each run was conducted with a different random split to ensure generalization of results.

\subsection{Dataset characteristics}
As a baseline, we measured how the anchors, positives and negatives were laid out in vector space based on character embeddings alone.  This gives us a measure of how difficult the problem is for the neural network to learn.  We indexed all the vector embeddings (regardless of test or train) into a nearest neighbors algorithm using the Spotify ANNOY\footnote{\url{https://github.com/spotify/annoy}} implementation.  We then queried the index for the $k$ nearest neighbors of this set, varying $k$ so it was either 20, 100, 500, or 1500 neighbors.  Our primary interest was in recall rates of positives prior to any training, to establish the baseline prior to training.  We also measured the nature of hard negatives as we varied the neighborhoods; i.e., what is the mean distance of negatives from the anchor while we increased neighborhoods, compared to the positive distances.  Figure \ref{people_characteristics} shows the results for the people data.  First, recall rate of positives in the nearest neighbor set was very low at 3\%, and it increased only to 6\% at a neighborhood size of 1500.  The difficulty of the problem for reconciling people's names is further highlighted by the distance data.  The mean distance of positives from anchor was 9.05, with a standard deviation of 3.08.  The mean distances of negatives from anchor was 2.73, with a standard deviation of 0.99 for $k$ of 20.  However even for $k$ of 1500, the mean negative distance was 3.64, well below the mean positive distance of 9.05.  The company data show a similar trend, although companies seems to be an easier problem than reconciling people data, as shown in Figure \ref{company_characteristics}.  Recall rate for companies starts at 16\% for a neighborhood size of 20, and is up to 25\% for a neighborhood size of 1500.  Mean negative distance is at 3.05 compared to 4.64 at a neighborhood size of 20, with a standard deviation of 1.44.  At a neighborhood size of 1500, mean negative sizes are slightly higher at 3.86.

### 2018-09-05 paper2018/evaluation.tex
fixing stuff

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The numbers for our adapted loss function were 81\% for people and 72\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies the only significant difference was that angular was worse.

 Precision is a little trickier to define, but one way is to measure it is to examine how many true matches we get in the neighborhood of each anchor before seeing a single mistake, i.e. a match that should not be there.  That metric gives a picture of how many names would be correctly found, on average, by a join.  Our loss function gives 62\% by this metric for people and 64\% for companies, so about two thirds of recalled names would be found before finding a single error.  Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.  For that, our loss yields 81\% for people and 73\% for companies.

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 80\%.  For companies, it is from 17\% to 72\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.  Precision at one improves from 10\% to 81\% for people and from 26\% to 73\% for companies.  In both these cases, demonstrable training occurred.

>>>>

\subsection{Performance for Joins}
For fuzzy joins, we need both precision and recall to be high.  Without good recall, a join will potentially miss names that should be joined.  Without high precision, a join will mistakenly join many inappropriate names.  The numbers for the adapted loss function were 81\% for people and 74\% for companies, so a join could capture most similar names.  For people, the adapted loss function showed overall better performance than triplet loss (see Table \ref{precision_recall}).  Furthermore, it appears that triplet loss outperformed improved loss, which in turn is better than angular loss for learning this problem.  On the other hand, for companies the only significant difference was that angular was worse.

 Precision is a little trickier to define, but one way is to measure it is to examine how many true matches we get in the neighborhood of each anchor before seeing a single mistake, i.e. a match that should not be there.  That metric gives a picture of how many names would be correctly found, on average, by a join.  Adapted loss is at 63\% by this metric for people and 66\% for companies, so about two thirds of recalled names would be found before finding a single error.  Since every name has at least one other name for the same entity, we also measure precision at 1, which is the probability that the very nearest neighbor is a true match.  For that, the very best performance we get is 84\% for people and 75\% for companies.

@@

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{distance}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 81\%.  For companies, it is from 16\% to 74\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 73\% for people and 16\% to 64\% for companies.  Precision@1 improves from 10\% to 81\% for people and from 26\% to 75\% for companies.  In both these cases, demonstrable training occurred.

### 2018-09-05 paper2018/introduction2.tex
fixing stuff

Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity.  For instance, the name of a person might be represented as \textit{Douglas Adams} and \textit{Douglas Noel Adams} or \textit{D. Adams} and \textit{Adams, Douglas}.  Similarly, ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

To test the feasibility of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).  The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.  Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}.  As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.  In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names have more stringent requirements for a join, as we describe below.

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen anchor and positive), and a large distance estimate for surface forms of different entities (an anchor and a negative).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  In other words, `hard negatives' dominate the space, and are the norm.  Our approach to the problem of triplet mining was therefore to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that suitable for use in joins than semi-hard triplet mining.

We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been proposed in the literature. 
%
%\begin{table}[!htb]
%    \caption{Example of a merge problem}
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table A}
%        \begin{tabular}{|l|l|}
%          \hline
%           Dept & Name \\
%           \hline
%           1    & Douglas Adams \\
%           2    & John Adams \\
%           3  & Douglas Bard \\
%           \hline
%        \end{tabular}
%    \end{subtable}%
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table B}
%        \begin{tabular}{|l|l|}
%          \hline
%           Name & Salary \\
%           \hline
%           Douglas Noel Adams & 2000 \\
%           Adams, John & 3000 \\
%           John Smith & 3000 \\
%           \hline
%        \end{tabular}
%    \end{subtable}
%    \label{table-example}
% \end{table}

>>>>

Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity.  For instance, the name of a person might be represented as \textit{Douglas Adams}, \textit{Douglas Noel Adams}, \textit{D. Adams} or \textit{Adams, Douglas}.  Similarly, ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

To test the feasibility of these ideas, we used Wikidata as ground truth to build models for datasets with 1.1M people's names (about 200K identities) and 130K company names (70K identities).  The problem of mapping vectors for the same entity closer in vector space than vectors for other entities is known in the literature as deep metric learning.  Deep metric learning is known to be a difficult problem as studied in the space of face recognition and person-re-identification \cite{DBLP:conf/cvpr/SchroffKP15}, \cite{8445716}, \cite{DBLP:journals/corr/abs-1802-03170}.  As a result, there is a significant amount of research on two aspects of training these networks: (a) how to choose samples for efficient learning, and (b) what constitutes a good loss function.  In building models for entity names, we had to adapt these techniques for triplet selection and loss functions because matching entity names has different characteristics, as we describe below.

As in face recognition, our system for metric learning is built by training a so-called triplet based `siamese triplet' network to learn to produce a small distance estimate for two surface forms for the same entity (between an arbitrarily chosen \textit{anchor} and \textit{positive}), and a large distance estimate for surface forms of different entities (an \textit{anchor} and a \textit{negative}).  A key problem in effective training of such networks is the problem of how to select negative pairs for training, because one cannot exhaustively show all negative pairs to the network.  In prior work for instance, this problem is solved by so-called `triplet mining' where so-called `semi-hard' negatives are gleaned after an all-pairs comparison of input vectors in a batch, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}.  `Semi-hard' negatives are negatives that are further away from the anchor than positives, but not by a sufficient margin.  The idea of focusing on semi-hard negatives is to avoid mining noisy regions of the embedding space.  However, for matching across entity names, most positive forms for the entity names are actually substantially further away from the anchor than are negatives, as we show empirically in this paper.  In other words, `hard negatives' dominate the space, and are the norm.  Our approach to the problem of triplet mining was therefore to use an approximate nearest neighbors algorithm to choose negatives for training that were in the nearest neighbor set, which means that most of the time, our negatives are `hard negatives', where the negative is closer to the anchor than positives.  This approach has three key benefits.  First, it lays out the entities based on their input vectors, and thus allows an efficient gathering of all nearest neighbors without a quadratic comparison of vectors in a batch to determine suitable negatives.  Second, it provides a baseline against which one can objectively measure the effects of training.  Third, it examines whether focusing on hard negatives is really detrimental to deep metric learning, at least for learning to map entity names in vector space.  As we show empirically in this paper, this technique is better for building models that are suitable for use in joins than semi-hard triplet mining when the dataset is dominated by hard negatives.  For easier datasets, the nearest neighbors approach was just as good as semi-hard training.

We also investigated the effect of using multiple local loss functions which have been proposed in the literature for improving deep metric learning, e.g., the triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, improved loss \cite{Zhang:2016:DML:3088616.3088665}, and angular loss \cite{DBLP:journals/corr/abs-1708-01682} functions.  For the problem of building models for datasets dominated by hard negatives, we found that an adaptation to the triplet loss function proposed in \cite{DBLP:conf/cvpr/SchroffKP15} was better than three other functions that have been used in the literature. 
%
%\begin{table}[!htb]
%    \caption{Example of a merge problem}
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table A}
%        \begin{tabular}{|l|l|}
%          \hline
%           Dept & Name \\
%           \hline
%           1    & Douglas Adams \\
%           2    & John Adams \\
%           3  & Douglas Bard \\
%           \hline
%        \end{tabular}
%    \end{subtable}%
%    \begin{subtable}{.5\linewidth}
%      \centering
%        \caption{Table B}
%        \begin{tabular}{|l|l|}
%          \hline
%           Name & Salary \\
%           \hline
%           Douglas Noel Adams & 2000 \\
%           Adams, John & 3000 \\
%           John Smith & 3000 \\
%           \hline
%        \end{tabular}
%    \end{subtable}
%    \label{table-example}
% \end{table}

### 2018-09-05 paper2018/joins.tex
adding minor changes
fixing stuff

%\section{Applying deep learning models to joins}
%\label{join_system}

@@

Assuming we have deep learning models that are trained to produce the right distance estimates for alternate surface forms for an entity, the models can be used for a join as follows.  For each cell value in the two columns to be joined, obtain vector embeddings from the last layer of the network.  Note that although the siamese network has three separate networks, each network is in fact identical to the other two networks because they share weights.  For the column cell values, vector embeddings are inserted into an approximate nearest neighbors index.  For each cell value in the right column, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index.  In our context, merging the datasets would involve joining the top $k$ rows in the left table that are `closest' in distance to each cell value in the right table.  Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but for most practical uses of join, $k$ is usually very small (typically 1).  This has implications on what metrics we can use to evaluate joins, as we describe in section \ref{results}.

>>>>

\section{Applying deep learning models to joins}
\label{join_system}

@@

Assuming we have deep learning models that are trained to produce the right distance estimates for alternate surface forms for an entity, the models can be used for a join as follows.  For each cell value in the two columns to be joined, obtain vector embeddings from the last layer of the network.  Note that although the siamese network has three separate networks, each network is in fact identical to the other two networks because they share weights.  For the left column cell values, vector embeddings are inserted into an approximate nearest neighbors index.  For each cell value in the right column, vector embeddings are used as `query vectors' to query the approximate nearest neighbors index.  In our context, merging the datasets would involve joining the top $k$ rows in the left table that are `closest' in distance to each cell value in the right table.  Note that the choice of $k$ clearly has a direct effect on the tradeoff between precision and recall, but for most practical uses of join, $k$ is usually very small (typically 1).  This has implications on what metrics we can use to evaluate joins, as we describe in the section \ref{results}.

### 2018-09-05 paper2018/main.tex
stuff
id
fixing stuff

@@

\maketitle
\begin{abstract}
Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to performing merges
based on deep learning models.  Our approach depends on (a) creating
a deep learning model that maps surface forms of an entity into a
set of vectors such that alternate forms for the same entity are
closest in vector space, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we had to adapt techniques from
metric learning due to the requirements of joins; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We found developed models that 
allow for joins with precision@1 of .75-.81 and
recall of .74-.81.  We make the models available to the community
for aligning people or companies across multiple datasets.  
\end{abstract}

>>>>

\author{Paper \#3597}

@@

\maketitle
\begin{abstract}
Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to performing merges
based on deep learning models.  Our approach depends on (a) creating
a deep learning model that maps surface forms of an entity into a
set of vectors such that alternate forms for the same entity are
closest in vector space, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we had to adapt techniques from
metric learning due to the characteristics of the data; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We developed models that 
allow for joins with precision@1 of .75-.81 and
recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.  
\end{abstract}

### 2018-09-05 paper2018/relatedWork.tex
fixing stuff

\section{Related Work}
Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF (e.g., \cite{Cohen2003}).  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches have emerged as a powerful alternative for merging data.  Data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be expressed as program transforms.

@@

Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/2014}, \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.  The closest approach to ours is the use of nearest neighbors algorithms for semi-hard triplet mining \cite{DBLP:journals/corr/KumarHC0D17}.  For semi-hard triplet mining, one cannot look at fixed neighborhood sizes in building triplets.  If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics.  Our focus on `hard negatives' means we can use a fixed $k$ to generate samples.  An additional benefit is that at least in the names domain, we show that metric learning with hard negatives is more effective than semi-hard mining.

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{DBLP:conf/cvpr/SongXJS16}, \cite{songCVPR17}.   Since we do not use batches in triplet selection, but rather neighborhoods, our loss function also operates with a global perspective.

>>>>

\section{Related Work}
Extensions in data management systems for handling joins typically use string similarity algorithms such as edit-distance, Jaro-Winkler and TF-IDF; e.g., \cite{Cohen2003}.  String matching algorithms often do not work for merging different forms of the same entity because valid transformations of entity names can yield very different strings.  More recently, data driven approaches have emerged as a powerful alternative for merging data.  Data driven approaches mine patterns to determine the `rules' for joining a given entity type.  One example of such an approach is illustrated in \cite{He:2015:SJS:2824032.2824036}, which determines which cell values should be joined based on whether those cell values co-occur on the same row across disparate tables in a very large corpus of data.  Another example is work by \cite{auto-join-joining-tables-leveraging-transformations} where program synthesis techniques are used to learn the right set of transformations needed to perform the entity matching operation.  Our approach for merging datasets is much more general than either approach because the mapping function generalizes the set of transformations that are allowed across surface forms of an entity, even if they cannot be directly expressed as program transforms.

@@

Metric learning is a well studied problem in the face recognition literature, e.g., \cite{DBLP:conf/cvpr/SchroffKP15}, with a rich literature in triplet mining techniques.  The closest approach to ours is the use of nearest neighbors algorithms for semi-hard triplet mining \cite{DBLP:journals/corr/KumarHC0D17}.  For semi-hard triplet mining, one cannot look at fixed neighborhood sizes in building triplets.  If all the positives are further away from the anchor than the negatives in a given neighborhood size of $k$, it means that $k$ needs to be expanded until a neighborhood size is found that has the right characteristics.  Our approach in including `hard negatives' means we can use a fixed $k$ to generate samples.  An additional benefit is that at least for certain types of datasets, we show that metric learning with hard negatives is more effective than semi-hard mining.

The study of loss function effectiveness in metric learning is also a rich literature, with two basic types of loss functions that have been proposed: (a) local loss functions such as triplet loss \cite{DBLP:conf/cvpr/SchroffKP15}, angular loss \cite{Zhang:2016:DML:3088616.3088665} and improved loss \cite{DBLP:journals/corr/abs-1708-01682}, and (b) loss functions that operate on a more global level across a batch of training examples \cite{NIPS2016_6200}, \cite{DBLP:conf/cvpr/SongXJS16}, \cite{songCVPR17}.   Since our triplet selection is global, rather than batch based, we did not see the value of using global loss functions.

### 2018-09-05 paper2018/siamese_networks.tex
figures
fixing stuff

These three input character embedding vectors were fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition. GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.

@@

Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions, three of which have been used in prior literature to explore their effectiveness for the entity metric learning problem.

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.3\linewidth}
        \centering
        \includegraphics[width=\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.3\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.3\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure}

@@

Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel
angular loss function which is not based on pairwise distances, but
rather is based on the angles of the triangle formed by the
\textit{anchor}, \textit{positive} and the \textit{negative} triplet.
Conceptually, they point out that since the \textit{anchor} and the
\textit{positive} pairs belong to the same class, the angle formed by
the \textit{anchor}, \textit{negative}, and \textit{positive} elements
should be as small as possible within that triangle.  Their loss
function is an attempt to minimize this angle, as defined in the
equations below.  The rough idea is that moving the positive nearer
and the \textit{negative} further away each reduce the angle, which we
illustrate in Figure~\ref{angular_loss} with the angle to shrink.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{p}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}

@@

The inspiration for adapting the original triplet loss is to separate the effect of the positive
and negative distances as much as possible.  Rather than subtracting
the negative distance from the positive one, we want to negate the
negative distance and then add the two.  To approximate this, we
subtract the negative distance from a margin, and use 0 instead if
that difference is negative.  We then combine the squared distances as
usual, as how in Figure~\ref{adapted}.

>>>>

These three input character embedding vectors were fed to three identical networks that share the same weights.  Weight sharing ensures that the networks learn the same mapping function.  In our implementation, each of the three networks had 4 stacked layers of 128 unit Gated Recurrent Units (or GRUs) to capture the sequential nature of the input.  GRUs are a type of recurrent network \cite{cho-al-emnlp14} where each hidden unit updates its weights at a specific step in the sequence $t$ based on the current input $x_t$ and the value of the hidden unit from the prior step $h_{t-1}$.  For name and textual data, positional information is critical, so we used GRUs instead of the convolutional neural networks (CNNs) that have been traditionally used in metric learning for face and image recognition.

@@

Let $\mathbf{x}$ represent an embedding for an entity name, and $\bf{x_{a}}$, $\bf{x_{p}}$, $\bf{x_{n}}$ reflect the vector embeddings of the \textit{anchor}, \textit{positive} and \textit{negative}, respectively.  We investigated four different loss functions, three of which have been used in prior face recognition literature to explore their effectiveness for the entity metric learning problem.

\begin{figure}[htb]
    \centering
    \begin{subfigure}[t]{0.31\linewidth}
        \centering
        \includegraphics[width=\linewidth]{schroff_triplet}
        \caption{Triplet loss}
        \label{schroff_loss}
    \end{subfigure}%
    ~ 
    \begin{subfigure}[t]{0.31\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{modified_loss}
        \caption{Modified loss}
        \label{modified_loss}
    \end{subfigure}
    ~ 
    \begin{subfigure}[t]{0.31\linewidth}
        \centering 
        \includegraphics[width=\linewidth]{angular_loss}
        \caption{Angular loss}
        \label{angular_loss}
    \end{subfigure}
    \caption{Loss functions}
\end{figure}

@@

Wang et al. \cite{DBLP:journals/corr/abs-1708-01682} define a novel
angular loss function which is not based on pairwise distances, but
rather is based on the angles of the triangle formed by the
\textit{anchor}, \textit{positive} and the \textit{negative} triplet.
Conceptually, they point out that since the \textit{anchor} and the
\textit{positive} pairs belong to the same class, the angle formed by
the \textit{anchor}, \textit{negative}, and \textit{positive} elements
should be as small as possible within that triangle.  Their loss
function is an attempt to minimize this angle, as defined in the
equations below.  The rough idea is that moving the \textit{positive} nearer
and the \textit{negative} further away each reduce the angle, which we
illustrate in Figure~\ref{angular_loss} with the angle to shrink.
\begin{equation}
\bf{x_{c}} = (\bf{x_{a}} + \bf{x_{p}}) / 2
\end{equation}
\begin{equation}
l_{triplet} = \left[[\bf{x_{a}} - \bf{x_{p}}\|^2 - 4 \tan^2 \alpha \|\bf{x_{n}} - \bf{x_{c}}\|^2 \right])_{+}
\end{equation}

@@

The inspiration for adapting the original triplet loss is to separate the effect of the positive
and negative distances as much as possible.  Rather than subtracting
the negative distance from the positive one, we want to negate the
negative distance and then add the two.  To approximate this, we
subtract the negative distance from a margin, and use 0 instead if
that difference is negative.  We then combine the squared distances as
usual, as shown in Figure~\ref{adapted}.  Note that we did not normalize $\|\bf{x} \| = 1$ because learning was worse with normalization.
